---
title: "`r schema$title`"
author: "`r author`"
date: `r date()`
geometry: margin=2cm
output: pdf_document
---


`r schema$description`

# Description of the annotation schema

Annotators can add further information they think require some attention
by adding further fields. These extra fields should start with \"note\".

## Basic elements

```{r basic, results="asis", echo=FALSE}

sections = names(schema$items$properties)
req = sections %in% schema$item$required
for (i in 1:length(sections)) {
	catElement(sections[i],schema$items$properties[[i]],1)
}

```

## EEG  section

An object with the following fields:

```{r eeg, results="asis", echo=FALSE}

sections = names(schema$items$properties$eeg$properties)
req = sections %in% schema$items$properties$eeg$required
for (i in 1:length(sections)) {
	catElementRec(sections[i],schema$items$properties$eeg$properties[[i]],0, req[i])
}

```

## Subjects  section

An array of objects with the following fields:

```{r subjects, results="asis", echo=FALSE}

sections = names(schema$items$properties$subjects$items$properties)
req = sections %in% schema$items$properties$subjects$items$required
for (i in 1:length(sections)) {
	catElementRec(sections[i],schema$items$properties$subjects$items$properties[[i]],0,req[i])
}

```

## Procedure  section

An object with the following fields:

```{r procedure, results="asis", echo=FALSE}

sections = names(schema$items$properties$procedure$properties)
req = sections %in% schema$items$properties$procedure$required
for (i in 1:length(sections)) {
	catElementRec(sections[i],schema$items$properties$procedure$properties[[i]],0,req[i])
}

```

## Data  section

An array of objects with the following fields

```{r data, results="asis", echo=FALSE}

sections = names(schema$items$properties$data$items$properties)
req = sections %in% schema$items$properties$data$items$required
for (i in 1:length(sections)) {
	catElementRec(sections[i],schema$items$properties$data$items$properties[[i]],0,req[i])
}

```


#  List of papers to be digitalized

```{r generateBibliography, results="asis", echo=FALSE}
for (i in 1:length(bib)) {
	cat(paste('**',names(bib[i]),'**: ', sep=''))
	print(bib[i], .opts=list(bib.style='authoryear'))
	cat('\n')
}
``` 


